### 2024-04-18 analysis/scripts/5_make_fig4.Rmd
update Fig 4

In QGIS open input_cutblocks and input_roads for TSA 27 as well as combined_revelstoke_roads.  Get Google satellite imagery from XYZ tile service.

@@

data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data/TSA27_real_cuts/dem"

@@

e_rds <- st_read(here::here(file.path(data_path_drvd, "../input_roads.gpkg")))
p_rds <- readRDS(here::here("analysis/data/derived_data/bench_results/result_mst_regular_1e-05_10_revelstoke_real.rds"))
o_rds <- st_read(here::here(file.path(data_path_drvd, "../../combined_revelstoke_roads.gpkg")))

>>>>

# run to save projected roads for use in QGIS
p_rds_mst <- readRDS(here::here("analysis/data/derived_data/bench_results/result_mst_regular_1e-05_10_revelstoke.rds"))

write_sf(p_rds_mst, here::here("analysis/data/derived_data/bench_results/mst_regular_1e-05_10_revelstoke.gpkg"))
```

In QGIS open input_cutblocks and input_roads for TSA 27 as well as combined_revelstoke_roads and projected roads for all cutblocks.  Get Google satellite imagery from XYZ tile service.

@@

```{r}
data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data/TSA27/dem"

@@

e_rds <- st_read(here::here(file.path(data_path_drvd, "../input_roads.gpkg")))
p_rds <- readRDS(here::here("analysis/data/derived_data/bench_results/result_mst_regular_1e-05_10_revelstoke.rds"))
o_rds <- st_read(here::here(file.path(data_path_drvd, "../../combined_revelstoke_roads.gpkg")))
